Empirical evidence for positive selection that is not adaptive evolution

### 2022-06-17 manuscript/main.tex
Table with proba of S > 1 for mutatations, SNPs and div in supp. mat.

    \section*{Acknowledgment}
    \label{sec:acknowledgment}
    We gratefully acknowledge the help of Nicolas Lartillot for his advice and review concerning this manuscript.
    This work was performed using the computing facilities of the CC LBBE/PRABI\@.
    \textbf{Funding:}
    Université de Lausanne;
    French National Research Agency, Grant ANR-19-CE12-0019 / HotRec.
    \textbf{Author contributions:}
    Original idea: T.L.\ and J.J.;
    Model conception: T.L., J.J.\ and N.S.;
    Code: T.L.;
    Data analyses: T.L.\ and J.J.;
    Interpretation: T.L., J.J.\ and N.S.;
    First draft, editing and revisions: T.L., J.J.\ and N.S.;
    Project management and funding: N.S\@.
    \textbf{Competing interests:}
    The authors declare no conflicts of interest.
    \textbf{Data and materials availability:}
    Snakemake pipeline, analysis scripts and documentation are available at \href{https://github.com/ThibaultLatrille/SelCoeff}{github.com/ThibaultLatrille/SelCoeff}.

>>>>

    \section*{Acknowledgment}
    \label{sec:acknowledgment}
    This work was performed using the computing facilities of the CC LBBE/PRABI\@.
    \textbf{Funding:}
    Université de Lausanne;
    \textbf{Author contributions:}
    Original idea: T.L.\ and J.J.;
    Model conception: T.L., J.J.\ and N.S.;
    Code: T.L.;
    Data analyses: T.L.\ and J.J.;
    Interpretation: T.L., J.J.\ and N.S.;
    First draft, editing and revisions: T.L., J.J.\ and N.S.;
    Project management and funding: N.S\@.
    \textbf{Competing interests:}
    The authors declare no conflicts of interest.
    \textbf{Data and materials availability:}
    Snakemake pipeline, analysis scripts and documentation are available at \href{https://github.com/ThibaultLatrille/SelCoeff}{github.com/ThibaultLatrille/SelCoeff}.

### 2022-06-17 manuscript/supp-mat.tex
Table with proba of S > 1 for mutatations, SNPs and div in supp. mat.

\title{Selection coefficients at the phylogenetic and population-genetic scale}

\author{
    \large
    T. {Latrille}$^{1}$, J. {Joseph}$^{2}$, N. {Salamin}$^{1}$\\
    $^{1}$Université de Lausanne, Lausanne, Switzerland
    $^{1}$Université de Lyon, Lyon, France
}

\begin{document}
    \maketitle
    \tableofcontents
    \clearpage

@@

    \begin{center}
        \begin{longtable}{|l|l|r|r|r|r|r|}
            \toprule
            Population           & Species             & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}(S > 0)$ & $\mathbb{P}_{obs}[S>0]$ & $\mathbb{P} [ \beta > 0 ]$ & $\mathbb{P} [ \beta > 0  | S>0]$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{7}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

@@

            Equus c.             & Equus caballus      & $ 0.002$              & $ 0.301$                  & $ 0.243$                & $ 0.113$                   & $ 0.793$                       \\
            Canis f.             & Canis familiaris    & $ 0.003$              & $ 0.421$                  & $ 0.181$                & $ 0.048$                   & $ 0.761$                       \\
            Iran                 & Bos taurus          & $ 0.005$              & $ 0.249$                  & $ 0.264$                & $ 0.098$                   & $ 0.605$                       \\
            Uganda               & Bos taurus          & $ 0.006$              & $ 0.254$                  & $ 0.249$                & $ 0.095$                   & $ 0.630$                       \\
            Australia            & Capra hircus        & $ 0.003$              & $ 0.286$                  & $ 0.265$                & $ 0.096$                   & $ 0.512$                       \\
            France               & Capra hircus        & $ 0.004$              & $ 0.285$                  & $ 0.274$                & $ 0.092$                   & $ 0.529$                       \\
            Iran (C. aegagrus)   & Capra hircus        & $ 0.004$              & $ 0.284$                  & $ 0.270$                & $ 0.095$                   & $ 0.455$                       \\
            Iran                 & Capra hircus        & $ 0.004$              & $ 0.297$                  & $ 0.239$                & $ 0.080$                   & $ 0.500$                       \\
            Italy                & Capra hircus        & $ 0.004$              & $ 0.285$                  & $ 0.265$                & $ 0.087$                   & $ 0.500$                       \\
            Morocco              & Capra hircus        & $ 0.004$              & $ 0.296$                  & $ 0.200$                & $ 0.080$                   & $ 0.509$                       \\
            Iran                 & Ovis aries          & $ 0.008$              & $ 0.229$                  & $ 0.259$                & $ 0.060$                   & $ 0.366$                       \\
            Iran (O. orientalis) & Ovis aries          & $ 0.009$              & $ 0.226$                  & $ 0.272$                & $ 0.067$                   & $ 0.344$                       \\
            Iran (O. vignei)     & Ovis aries          & $ 0.008$              & $ 0.235$                  & $ 0.307$                & $ 0.075$                   & $ 0.464$                       \\
            Various              & Ovis aries          & $ 0.009$              & $ 0.226$                  & $ 0.279$                & $ 0.065$                   & $ 0.378$                       \\
            Morocco              & Ovis aries          & $ 0.008$              & $ 0.225$                  & $ 0.212$                & $ 0.054$                   & $ 0.377$                       \\
            Barbados             & Chlorocebus sabaeus & $ 0.004$              & $ 0.314$                  & $ 0.258$                & $ 0.109$                   & $ 0.670$                       \\
            Central Afr. Rep.    & Chlorocebus sabaeus & $ 0.006$              & $ 0.315$                  & $ 0.264$                & $ 0.094$                   & $ 0.619$                       \\
            Ethiopia             & Chlorocebus sabaeus & $ 0.005$              & $ 0.307$                  & $ 0.252$                & $ 0.107$                   & $ 0.660$                       \\
            Gambia               & Chlorocebus sabaeus & $ 0.005$              & $ 0.303$                  & $ 0.249$                & $ 0.085$                   & $ 0.666$                       \\
            Kenya                & Chlorocebus sabaeus & $ 0.006$              & $ 0.311$                  & $ 0.272$                & $ 0.095$                   & $ 0.602$                       \\
            Nevis                & Chlorocebus sabaeus & $ 0.004$              & $ 0.302$                  & $ 0.252$                & $ 0.102$                   & $ 0.642$                       \\
            South Africa         & Chlorocebus sabaeus & $ 0.007$              & $ 0.312$                  & $ 0.246$                & $ 0.094$                   & $ 0.638$                       \\
            Saint Kitts          & Chlorocebus sabaeus & $ 0.004$              & $ 0.306$                  & $ 0.250$                & $ 0.106$                   & $ 0.664$                       \\
            Zambia               & Chlorocebus sabaeus & $ 0.006$              & $ 0.308$                  & $ 0.261$                & $ 0.103$                   & $ 0.630$                       \\
            African              & Homo sapiens        & $ 0.003$              & $ 0.256$                  & $ 0.141$                & $ 0.103$                   & $ 1.000$                       \\
            Admixed American     & Homo sapiens        & $ 0.002$              & $ 0.247$                  & $ 0.145$                & $ 0.103$                   & $ 0.945$                       \\
            East Asian           & Homo sapiens        & $ 0.002$              & $ 0.241$                  & $ 0.129$                & $ 0.098$                   & $ 0.918$                       \\
            European             & Homo sapiens        & $ 0.002$              & $ 0.254$                  & $ 0.130$                & $ 0.098$                   & $ 0.919$                       \\
            South Asian          & Homo sapiens        & $ 0.002$              & $ 0.246$                  & $ 0.131$                & $ 0.096$                   & $ 0.912$                       \\

@@

        \item $\mathbb{P}_{div}(S > 0)$ is the proportion of substitution in the terminal branch observed with a selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.
        \item $\mathbb{P}_{obs}[S>0]$ is the proportion of SNPs observed with a predicted selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.
        \item $\mathbb{P} [ \beta > 0 ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) larger than 1, estimated for the whole genome.
        \item $\proba [ \polyAdv | \divAdv]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) larger than 1, estimated on the subset of SNPs observed with a predicted selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.

>>>>

\title{Empirical evidence for positive selection that is not adaptive evolution}

\author{
    \large
    T. {Latrille}, J. {Joseph}, N. {Salamin}\\
}

\begin{document}
    \maketitle
    \part*{Supplementary materials}
    \tableofcontents
    \clearpage

@@

    \begin{center}
        \begin{longtable}{|l|l|r|r|r|r|}
            \toprule
            Population           & Species             & Tajima $\theta_{\pi}$ & $\mathbb{P}_{mut}[S>0]$ & $\mathbb{P}_{poly}[S>0]$ & $\mathbb{P}_{div}[S>0]$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{6}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

@@

            Equus c.             & Equus caballus      & $ 0.002$              & $ 0.054$                & $ 0.243$                 & $ 0.301$                \\
            Canis f.             & Canis familiaris    & $ 0.003$              & $ 0.049$                & $ 0.181$                 & $ 0.423$                \\
            Iran                 & Bos taurus          & $ 0.005$              & $ 0.053$                & $ 0.264$                 & $ 0.266$                \\
            Uganda               & Bos taurus          & $ 0.006$              & $ 0.053$                & $ 0.249$                 & $ 0.267$                \\
            Australia            & Capra hircus        & $ 0.003$              & $ 0.054$                & $ 0.265$                 & $ 0.301$                \\
            France               & Capra hircus        & $ 0.004$              & $ 0.054$                & $ 0.274$                 & $ 0.301$                \\
            Iran (C. aegagrus)   & Capra hircus        & $ 0.004$              & $ 0.054$                & $ 0.270$                 & $ 0.301$                \\
            Iran                 & Capra hircus        & $ 0.004$              & $ 0.054$                & $ 0.239$                 & $ 0.303$                \\
            Italy                & Capra hircus        & $ 0.004$              & $ 0.054$                & $ 0.265$                 & $ 0.301$                \\
            Morocco              & Capra hircus        & $ 0.004$              & $ 0.054$                & $ 0.200$                 & $ 0.303$                \\
            Iran                 & Ovis aries          & $ 0.008$              & $ 0.054$                & $ 0.259$                 & $ 0.229$                \\
            Iran (O. orientalis) & Ovis aries          & $ 0.009$              & $ 0.054$                & $ 0.272$                 & $ 0.226$                \\
            Iran (O. vignei)     & Ovis aries          & $ 0.008$              & $ 0.054$                & $ 0.307$                 & $ 0.235$                \\
            Various              & Ovis aries          & $ 0.009$              & $ 0.054$                & $ 0.279$                 & $ 0.226$                \\
            Morocco              & Ovis aries          & $ 0.008$              & $ 0.054$                & $ 0.212$                 & $ 0.225$                \\
            Barbados             & Chlorocebus sabaeus & $ 0.004$              & $ 0.050$                & $ 0.258$                 & $ 0.305$                \\
            Central Afr. Rep.    & Chlorocebus sabaeus & $ 0.006$              & $ 0.050$                & $ 0.264$                 & $ 0.307$                \\
            Ethiopia             & Chlorocebus sabaeus & $ 0.005$              & $ 0.050$                & $ 0.252$                 & $ 0.305$                \\
            Gambia               & Chlorocebus sabaeus & $ 0.005$              & $ 0.050$                & $ 0.249$                 & $ 0.307$                \\
            Kenya                & Chlorocebus sabaeus & $ 0.006$              & $ 0.050$                & $ 0.272$                 & $ 0.309$                \\
            Nevis                & Chlorocebus sabaeus & $ 0.004$              & $ 0.050$                & $ 0.252$                 & $ 0.305$                \\
            South Africa         & Chlorocebus sabaeus & $ 0.007$              & $ 0.050$                & $ 0.246$                 & $ 0.309$                \\
            Saint Kitts          & Chlorocebus sabaeus & $ 0.004$              & $ 0.050$                & $ 0.250$                 & $ 0.309$                \\
            Zambia               & Chlorocebus sabaeus & $ 0.006$              & $ 0.050$                & $ 0.261$                 & $ 0.307$                \\
            African              & Homo sapiens        & $ 0.003$              & $ 0.051$                & $ 0.141$                 & $ 0.259$                \\
            Admixed American     & Homo sapiens        & $ 0.002$              & $ 0.051$                & $ 0.145$                 & $ 0.258$                \\
            East Asian           & Homo sapiens        & $ 0.002$              & $ 0.051$                & $ 0.129$                 & $ 0.259$                \\
            European             & Homo sapiens        & $ 0.002$              & $ 0.051$                & $ 0.130$                 & $ 0.258$                \\
            South Asian          & Homo sapiens        & $ 0.002$              & $ 0.051$                & $ 0.131$                 & $ 0.259$                \\

@@

        \item $\mathbb{P}_{mut}[S>0]$ is the proportion of mutational opportunities with a predicted selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.
        \item $\mathbb{P}_{poly}[S>0]$ is the proportion of SNPs observed with a predicted selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.
        \item $\mathbb{P}_{div}[S>0]$ is the proportion of substitution in the terminal branch observed with a selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.

    \begin{center}
        \begin{longtable}{|l|l|r|r|r|r|}
            \toprule
            Population           & Species             & Tajima $\theta_{\pi}$ & $\mathbb{P}_{mut}[S>1]$ & $\mathbb{P}_{poly}[S>1]$ & $\mathbb{P}_{div}[S>1]$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{6}{r}{{Continued on next page}} \\
            \midrule
            \endfoot
            Equus c.             & Equus caballus      & $ 0.002$              & $ 0.018$                & $ 0.098$                 & $ 0.113$                \\
            Canis f.             & Canis familiaris    & $ 0.003$              & $ 0.014$                & $ 0.070$                 & $ 0.167$                \\
            Iran                 & Bos taurus          & $ 0.005$              & $ 0.017$                & $ 0.111$                 & $ 0.105$                \\
            Uganda               & Bos taurus          & $ 0.006$              & $ 0.017$                & $ 0.104$                 & $ 0.107$                \\
            Australia            & Capra hircus        & $ 0.003$              & $ 0.017$                & $ 0.103$                 & $ 0.122$                \\
            France               & Capra hircus        & $ 0.004$              & $ 0.017$                & $ 0.106$                 & $ 0.122$                \\
            Iran (C. aegagrus)   & Capra hircus        & $ 0.004$              & $ 0.017$                & $ 0.103$                 & $ 0.123$                \\
            Iran                 & Capra hircus        & $ 0.004$              & $ 0.017$                & $ 0.092$                 & $ 0.124$                \\
            Italy                & Capra hircus        & $ 0.004$              & $ 0.017$                & $ 0.103$                 & $ 0.122$                \\
            Morocco              & Capra hircus        & $ 0.004$              & $ 0.017$                & $ 0.079$                 & $ 0.124$                \\
            Iran                 & Ovis aries          & $ 0.008$              & $ 0.018$                & $ 0.102$                 & $ 0.102$                \\
            Iran (O. orientalis) & Ovis aries          & $ 0.009$              & $ 0.018$                & $ 0.107$                 & $ 0.099$                \\
            Iran (O. vignei)     & Ovis aries          & $ 0.008$              & $ 0.018$                & $ 0.121$                 & $ 0.103$                \\
            Various              & Ovis aries          & $ 0.009$              & $ 0.018$                & $ 0.114$                 & $ 0.100$                \\
            Morocco              & Ovis aries          & $ 0.008$              & $ 0.018$                & $ 0.084$                 & $ 0.099$                \\
            Barbados             & Chlorocebus sabaeus & $ 0.004$              & $ 0.015$                & $ 0.102$                 & $ 0.126$                \\
            Central Afr. Rep.    & Chlorocebus sabaeus & $ 0.006$              & $ 0.015$                & $ 0.106$                 & $ 0.124$                \\
            Ethiopia             & Chlorocebus sabaeus & $ 0.005$              & $ 0.015$                & $ 0.097$                 & $ 0.123$                \\
            Gambia               & Chlorocebus sabaeus & $ 0.005$              & $ 0.015$                & $ 0.101$                 & $ 0.127$                \\
            Kenya                & Chlorocebus sabaeus & $ 0.006$              & $ 0.015$                & $ 0.105$                 & $ 0.128$                \\
            Nevis                & Chlorocebus sabaeus & $ 0.004$              & $ 0.015$                & $ 0.102$                 & $ 0.125$                \\
            South Africa         & Chlorocebus sabaeus & $ 0.007$              & $ 0.015$                & $ 0.098$                 & $ 0.125$                \\
            Saint Kitts          & Chlorocebus sabaeus & $ 0.004$              & $ 0.015$                & $ 0.099$                 & $ 0.126$                \\
            Zambia               & Chlorocebus sabaeus & $ 0.006$              & $ 0.015$                & $ 0.104$                 & $ 0.123$                \\
            African              & Homo sapiens        & $ 0.003$              & $ 0.015$                & $ 0.057$                 & $ 0.104$                \\
            Admixed American     & Homo sapiens        & $ 0.002$              & $ 0.015$                & $ 0.058$                 & $ 0.103$                \\
            East Asian           & Homo sapiens        & $ 0.002$              & $ 0.015$                & $ 0.052$                 & $ 0.104$                \\
            European             & Homo sapiens        & $ 0.002$              & $ 0.015$                & $ 0.052$                 & $ 0.103$                \\
            South Asian          & Homo sapiens        & $ 0.002$              & $ 0.015$                & $ 0.051$                 & $ 0.104$                \\
        \item $\mathbb{P}_{mut}[S>1]$ is the proportion of mutational opportunities with a predicted selection coefficient at the phylogenetic scale ($\Sphy$) larger than 1.
        \item $\mathbb{P}_{poly}[S>1]$ is the proportion of SNPs observed with a predicted selection coefficient at the phylogenetic scale ($\Sphy$) larger than 1.
        \item $\mathbb{P}_{div}[S>1]$ is the proportion of substitution in the terminal branch observed with a selection coefficient at the phylogenetic scale ($\Sphy$) larger than 1.
